```{r import library}

library(ggplot2)
```

```{r first example}
ds <- read.csv("https://github.com/ripberjt/qrmlabs/raw/master/Class%20Data%20Set%20Factored.csv", header = TRUE)

ggplot(ds, aes(age)) +
  geom_histogram()


ggplot(ds) +
  geom_histogram(aes(x=age, y=..density..))


ggplot(ds, aes(age)) +
  geom_histogram(aes(x=age, y=..density..), bins=50) +
  stat_function(fun=dnorm, args = list(mean=mean(ds$age), sd=sd(ds$age)), color="red")


set.seed(357)
x <- data.frame(name = as.factor(sample(letters, 10)), val = runif(10))
x
```

There are four basic parts of a simple data visualization in ggplot2: the _ggplot()_ function, the _data_ parameter, the _aes()_ function, and the geom specification

ggplot(data = ___, aes(x = ___, y = ___)) + geom_line()

ggplot() function: initiates plotting

data: enables you to specify the dataframe that contains your data, with the variables that you want to visualize

geometric objects (eg geom_line, geom_boxplot ...): a geom is something you draw. It's short for geometric object. 

aes() function: enables you to create a set of mappings from data in your dataframe to the aesthetic attributes of the plot
geoms (geometric objects) have aesthetic attributes, things like colour and size. If you draw a point (point geom), that point will have attributes like the colour and size.
When we create a data visualization, we're connecting the data in a dataset to elements in visualization.
We create a mapping that connects the variables in a dataset to the aesthetic attributes of the geometric objects that we draw
The aes() function is the function that creates those mappings.


The syntax of facet_wrap

ggplot(data = Credit, aes(x = Balance)) + geom_density() +
facet_wrap(~Student)



```{r facet_wrap}
# You can facet by multiple variables
xp <- ggplot(mpg, aes(displ, hwy)) +
  geom_point() +
  facet_wrap(vars(cyl, drv))
xp

```